\huge Tor's Usability for Censorship Circumvention

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Formatting.

Other changes improve empirical goals from Section~\ref{sec:goals}: task completion, time to completion, and safe for high-risk users. 5-6 improve task completion, 7-8 reduce time to completion, and 9-10 builds users' mental models of censorship circumvention and network components involved. Users' full control of the configuration process remains preserved.\\

>>>>

Other changes improve empirical goals from Section~\ref{sec:goals}: task completion, time to completion, and safe for high-risk users. Items 5 and~6 improve task completion; 7 and~8 reduce time to completion; and 9 and~10 build users' mental models of censorship circumvention and the network components involved. Users' full control of the configuration process remains preserved.\\
